---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above. These can be installed with:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_deps()
```

# Setup

Remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
library(targets)
library(tarchetypes)

# Load our custom functions
library(purrr)
functions <- list.files(here::here("R"), full.names = TRUE)
purrr::walk(functions, source)
rm("functions")
tar_option_set(packages = c("purrr", "here", "jsonlite"))
```

# Targets

- Read the parameters for a single country

```{targets params, tar_simple = TRUE}
purrr::map(
  list.files(here::here("input"), full.names = TRUE), jsonlite::read_json
)
```

- Synthesize a population with 4 strains of an infectious disease using the parameters we just read in for each country

```{targets synthesize-population}
tar_target(
  pop,
  do.call(synthesize_population, params[[1]]),
  map(params)
)
```

- Summarise by country.

```{targets pop_sum, tar_simple = TRUE}
aggregate_dataframe(outcome ~ country, pop, calculate_quantiles)
```

- Plot the number of infections by risk group per individual in the population.

```{targets plot_population}
tar_target(
  plot_population,
  {
    plot <- plot_infections(pop)
    add_summary_to_infections_plot(plot, pop_sum)
  }
)
```

- Save the plot to the output directory.

```{targets save_pop_plot}
tar_file(
  save_pop_plot,
  save_plot(
    plot = plot_population, file = "population.png", path = "output"
  )
)
```

# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r, eval = FALSE}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r, message = FALSE, eval = FALSE}
tar_read(pop_sum)
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r, eval = FALSE}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
